Geometric variational problems

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
yny specific aim 1

Hamm and Kozlov (HK) pioneered 
the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
is widely used to describe biological phenomona 
fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
\cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
Recently, there has been a revival in interest in the HK theory as the quadratic assumption
for the elasticity energy density has caused
researchers to question the applicability of the theory 
for large curvatures
\cite{PhysRevLett.117.188102, ARGUDO20161619}.
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.  
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%

@@

The HK framework assumes a three-dimensional lipid monolayers with internal structure
consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
elastic energy density ${\cal W}$ that is quadratic in the Green-Lagrange strain tensor for membrane deformation of
this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy decomposes into four fundamental and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal:
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  As an illustration, the
lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%as a result of  %having a relatively long acyl chain. 
and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
because the addition of a positive splay 
to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
The subtraction of $k_0^2$ makes the energy distortion free
\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HARP model to estimate elastic moduli}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of the elastic moduli $\KB$,
$\KT$, $\KG$ and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium configuration \cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial configuration of a lipid bilayer patch contains only
splay deformation without any other components (saddle splay, twist and tilt). 
As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease,
and because the saddle splay, twist and tilt stay zeros, the slope gives the bending modulus in this case.

@@

%for a wide range of particle parameters and physical parameters in HARP to 
%
%We will also determine the effective saddle splay modulus $\KG$. 
The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
the saddle splay energy is largely invariant under shape changes.
To evaluate $\KG$, we will combine the present particle simulations with the string method 
from PI-RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
More generally, PI-RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
As a result, saddle splay can quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
%Using the string method, we will evaluate the transition energies between the intact pancake shape,
%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
%
%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
%

@@

\subsubsection{HK elastic energy form}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researcher have assumed that $\KT = 0$ because of the relationship between twist the assumption of lateral fluidity in membranes 
\cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
  \textbf{(ii)}
Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
Later, \cite{C9SM02079A} 
and \cite{PhysRevE.102.042406} independently identified an inconsistency an the argument used by \cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In \cite{RyKlYaCo16}, the PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
  \textbf{(iii)}
  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
  and accounting for these couplings by Taylor expansion  
  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.

The form of the elastic energy density \eqref{ansatz3} is the same as
  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
  Using this observation, we prove an exact identity 
  that gives the incompressility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.

%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%  This gives the continuum elastic energy equals
%  \begin{equation}
%    \label{eq:twist_energy}
%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%  \end{equation}
%  which we compare to the HAP simulation data.

%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$}
%The HAP energy converges to the surface energy in the limit of vanishing screening length 
%and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
%area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
%PI RR has worked directly on phase field approximations of membrane bending energy 
%\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
%The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
%
%We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
%%The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
%%The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
%%to the characteristic function of a set solving a perimeter minimization problem 
%%\cite{Modica87, MODICA1987487, LuMo89}. 
%%
%%
%One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
%\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
%\begin{equation}
%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
%\end{equation}
%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
%\cite{https://doi.org/10.1038/s41467-019-09787-6}

% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
% whether \eqref{ansatz3} contains a complete list of consistent deformations.
%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
%  \textbf{(ii)}
%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
%  Later, \cite{C9SM02079A} 
%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
%  from a transversal tilt invariance assumption.
%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
%  \textbf{(iii)}
%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
%suggesting a somewhat smaller magnitude for $\KG$.

>>>>

Hamm and Kozlov (HK) pioneered 
the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
is widely used to describe biological phenomona 
fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
\cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
Recently, there has been a revival in interest in the HK theory as the quadratic assumption
for the elasticity energy density has caused
researchers to question the applicability of the theory 
for large curvatures
\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

@@

The HK framework assumes a three-dimensional lipid monolayers with internal structure
consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
elastic energy density ${\cal W}$ that is quadratic in the Green-Lagrange strain tensor for membrane deformation of
this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy decomposes into four fundamental and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal:
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
%As an illustration, the
%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%%as a result of  %having a relatively long acyl chain. 
%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
%because the addition of a positive splay 
%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
%The subtraction of $k_0^2$ makes the energy distortion free
%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of the elastic moduli $\KB$,
$\KT$, $\KG$ and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium configuration \cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial configuration of a lipid bilayer patch contains only
splay deformation without any other components (saddle splay, twist and tilt). 
As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease,
and because the saddle splay, twist and tilt stay zero, the slope gives the bending modulus in this case.

@@

%for a wide range of particle parameters and physical parameters in HARP to 
%
%We will also determine the effective saddle splay modulus $\KG$. 
The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
the saddle splay energy is largely invariant under shape changes.
To evaluate $\KG$, we will combine the present particle simulations with the string method 
from PI RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
As a result, saddle splay can quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
%Using the string method, we will evaluate the transition energies between the intact pancake shape,
%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
%
%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
%

@@

%\subsubsection{HK elastic energy form}
\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researcher have assumed that $\KT = 0$ because of the relationship between twist the assumption of lateral fluidity in membranes 
\cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
%A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)}
Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
Later, \cite{C9SM02079A} 
and \cite{PhysRevE.102.042406} independently identified an inconsistency an the argument used by \cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In \cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
  \textbf{(iii)}
  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}, which gives rise to a larger energy barrier for monolayer fusion than is found by experiments \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

 The form of the elastic energy density \eqref{ansatz3} is the same as
  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
  Based on this observation, we propose to examine the HK analysis to resolve the aforementioned inconsistencies: We expand the strain tensor in terms of a plane
  perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as done in the past works) so that the gradient terms in the elastic energy completely decouple. 
  Using this expansion we prove an exact identity 
  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing screening length 
and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
PI RR has worked directly on phase field approximations of membrane bending energy 
\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.

We will develop the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
to the characteristic function of a set solving a perimeter minimization problem 
\cite{Modica87, MODICA1987487, LuMo89}. 
%
%
One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
%\begin{equation}
%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
%\end{equation}
%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
%\cite{https://doi.org/10.1038/s41467-019-09787-6}
%
%
%% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
%% whether \eqref{ansatz3} contains a complete list of consistent deformations.
%%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
%%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
%%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
%%  \textbf{(ii)}
%%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
%%  Later, \cite{C9SM02079A} 
%%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
%%  from a transversal tilt invariance assumption.
%%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
%%  \textbf{(iii)}
%%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
%%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
